---
title: "Diet analysis"
author: "Julien Christophe Piquet"
date: "21/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = F)
```

# **DATA FORMATION**

```{r folder}
folder_data<-"E:/Research/Projects/A_2019_CSIC_TROPHIC/Research/Data"
```

# **Basic diet information**

We first prepare the data.

```{r data indices}
library(readxl)
raw_reads<-read_excel(paste0(folder_data,sep="/","raw_read_table.xlsx"))
raw_reads[is.na(raw_reads$Orden),]$Orden<-"Other" # replacing empty order by Other

# Presence-absence table

raw_presence<-raw_reads
raw_presence[,2:46]<-apply(raw_reads[,2:46],2, function(x) ifelse(x>0,1,0)) # changing reads to binary presence-absence
```

We now calculate the number of orders detected and the number of OTUs per species.

```{r basic diet information}
length(unique(raw_reads$Orden)) # number of orders including undetermined taxa (number of assigned orders plus one)

table<-as.data.frame(cbind(reads=apply(raw_presence[,2:46],2,sum),
             species=substr(colnames(raw_presence[,2:46]),1,2))) # generating reads counts per species
table$reads<-as.numeric(table$reads)
tapply(table$reads,table$species,mean)
tapply(table$reads,table$species,sd)
```

# **Diet indices calculation**

We calculate the relative read abundance.

```{r rra calculation}
rra_table<-cbind(raw_reads[,1],
                 may=apply(raw_reads[,c(2:6,17:21,32:36),],1,sum),
                 aug=apply(raw_reads[,c(7:11,22:26,37:41),],1,sum),
                 nov=apply(raw_reads[,c(12:16,27:31,42:46),],1,sum),
                 raw_reads[,51]) # collapsing reads per month across all species
rra_table<-do.call(cbind,lapply(rra_table[,2:4],function(x) tapply(x,rra_table$Orden,sum))) #counting reads per order and generating table
rra_table<-as.data.frame(rra_table)
rra_table$total<-apply(rra_table[,1:3],1,sum) #year-round reads abundance
rra_table<-cbind(rra_table,
                 do.call(cbind,lapply(rra_table[,1:4],function(x) 
                   (x/sum(x))*100))) #rra calculation per order
colnames(rra_table)<-c(colnames(rra_table[,1:4]),paste0("rra","_",colnames(rra_table[,1:4])))
```

We calculate the percentage of frequency of occurrence.

```{r %foo calculation}
foo_table<-do.call(cbind,lapply(raw_presence[,2:46], function(x) tapply(x,raw_presence$Orden,max))) # determining presence-absence per sample and order
foo_table<-cbind(may=apply(foo_table[,c(1:5,16:20,31:35)],1,sum),
                 aug=apply(foo_table[,c(6:10,21:25,36:40)],1,sum),
                 nov=apply(foo_table[,c(11:15,26:30,41:45)],1,sum)) # calculating number of samples where each order is present
foo_table<-as.data.frame(foo_table)
foo_table$total<-apply(foo_table,1,sum) # number of samples where each order is present across the year
foo_table<-cbind(foo_table,
                 do.call(cbind,lapply(foo_table[,1:3],function(x)
                   (x/15)*100))) # %FOO calculation for each month
colnames(foo_table)<-c(colnames(foo_table[,1:4]),paste0("foo","_",colnames(foo_table[,1:3])))
foo_table$foo_total<-(foo_table$total/45)*100 # %FOO for the whole year
```

We now obtain percentage of occurrence.

```{r poo calculation}
poo_table<-foo_table[,1:4] 
poo_table<-cbind(poo_table,
                 do.call(cbind,lapply(poo_table[,1:4],function(x)
                   (x/sum(x))*100))) # POO calculation
colnames(poo_table)<-c(colnames(poo_table[,1:4]),paste0("poo","_",colnames(poo_table[,1:4])))
```

We now extract a global table and calculate mIRI.

```{r global table and mIRI}
data_index_diet<-cbind(rra_table,foo_table[,1:ncol(foo_table)],poo_table[,5:ncol(poo_table)])
colnames(data_index_diet)[c(1:4,9:12)]<-c(paste0("reads","_",colnames(data_index_diet[,1:4])),paste0("presence","_",colnames(data_index_diet[,9:12])))

# mIRI calculation

data_index_diet<-cbind(data_index_diet,
                     do.call(cbind,list(mapply(
                       function(x,y) ((x*y)/sum(x*y))*100,
                       x=data_index_diet[,5:8],
                       y=data_index_diet[,17:20]
                     ))))

colnames(data_index_diet)[21:24]<-c("miri_may","miri_aug","miri_nov","miri_total")
data_index_diet$order<-row.names(data_index_diet)
data_index_diet<-data_index_diet[,c(which(colnames(data_index_diet)=="order"),seq(1,ncol(data_index_diet)-1,1))]
rownames(data_index_diet)<-seq(1,nrow(data_index_diet),1)

write.csv(data_index_diet,file=paste0(folder_data,"/","data_index_diet.csv"))
```

We prepare the data for subsequent analyses.

```{r data}
data<-data_index_diet[,-c(2:5,10:13)]
```

# **ANALYSIS**

## **Data preparation**

```{r data preparation for analyses}
other<-data[data$order=="Other",]
data<-data[data$order!="Other",] # we remove undertermined groups
```

## **RRA, POO and mIRI per orders**

```{r summary descriptions}
head(data[,c(1,5)][order(data$rra_total,decreasing = T),])
head(data[,c(1,16)][order(data$poo_total,decreasing = T),])
head(data[,c(1,17)][order(data$miri_total,decreasing = T),])
```

## **Correlation RRA and POO**

```{r correlation tests}
with(data,cor.test(rra_may,poo_may,method="spearman"))
with(data,cor.test(rra_aug,poo_aug,method="spearman"))
with(data,cor.test(rra_nov,poo_nov,method="spearman"))
with(data,cor.test(rra_total,poo_total,method="spearman"))
```

## **Grouping analysis**

```{r grouping}
library(cluster)
library(factoextra)
library(car)
library(onewaytests)
library(dplyr)

# Cluster
clusters<-kmeans(data[,17],3,nstart=100)
data$cluster<-clusters$cluster
tapply(data$miri_total,data$cluster,mean)
data$cluster<-recode_factor(data$cluster,'3'="high",'2'="moderate",'1'="low")

other$cluster<-NA
data<-rbind(data,other)

write.csv(data,file=paste0(folder_data,sep="/","data_index_diet.csv"))

# Comparing mIRI per cluster
with(data,leveneTest(miri_total,cluster))
welch<-welch.test(miri_total~cluster,data=data,rate=0.1)
paircomp(welch, adjust.method = "holm")
tapply(data$miri_total,data$cluster,mean)
tapply(data$miri_total,data$cluster,sd)
```

